Contention Management for 5G

### 2017-02-20 article/article.tex
dessin

     \todo{Dire après  la définition des problèmes qu'on pourrait demander de trouver l'assignement et même le routage pour optimiser, mais pas dans cet article
     et qu'on travail avec des réseaux déjà constitués}
      \todo{Si on s'en sert, ajouter ici que le routage est cohérent.}

@@

      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$. The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in {\cal R}$ at its source.
      A $(P,\tau)$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}$, that is $\forall (r_i, r_j) \in {\cal R_{\cal C}}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$, 
      we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$

@@

%       A {\bf conflict graph} represents the collision between the routes of $ {\cal R}_{\cal C}$. The vertices of a conflict graph $G = (V,E)$ are the routes of $ {\cal R}_{\cal C}$, and there is an edge between two vertices if and only if there is a common arc between the two routes in $ {\cal R}_{\cal C}$.
%       
%       Given $u$ and $v$ two vertices of the conflict graph, corresponding to two routes colliding in $ {\cal R}_{\cal C}$. The weight of an edge, $w(u,v)$, is the absolute value of the difference between the distance of the two routes between their respective source node and the collision point.
%       
%       A labeling $F$ of such a graph is an affectation of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.
      \begin{figure}[h]
       \begin{center}
      \includegraphics[scale=0.7]{Fig5.pdf}
      \end{center}
       \caption{A routage graph with $(0,\dots,0)$ as a $(2,1)$-periodic affectation}
      \end{figure}

@@

	\begin{lemma} 
	 For any odd $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
	\end{lemma}
\begin{proof}

      Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
      We change the delays so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$. In such a graph, there is no $(P,\tau)$-periodic affectation, because of $P < n$.\\
      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.

@@

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
      and two disjoint subsets of vertices $S$ and $T$ of equal cardinality, where $S$ is the set of RRHs and $T$ is the set of BBUs. 
      A \textbf{symmetric} assignment ${\cal C}$, is an involutive function from $S$ to $T$, which maps each element $s\in S$ to ${\cal C}(s)$ and ${\cal C}(s)$ to $s$. It can also be seen as the set of pairs $(s,{\cal C}(s))$ and $({\cal C}(s),s)$.\\
      The Routing function ${\cal R}$ associtates to each couple $(s,{\cal C}(s))$ a route called $r_s$ and to each couples $({\cal C}(s),s)$ a route called $r_{{\cal C}(s)}$.\\     
       We are given a period $P$, a routing function ${\cal R}$, and we consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_s$ to the route $r_s$ which begins by $s$.  This affectation represents the following process: first a message is sent at $s$, through the route $r_s$, at time $m_s$.

>>>>

      \todo{Si on s'en sert, ajouter ici que le routage est cohérent.}

@@

      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R_{\cal C}$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R_{\cal C}$. The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in \cal R_{\cal C}$ at its source.
      A $(P,\tau)$-periodic affectation must have no {\bf collision} between two routes in $\cal R_{\cal C}$, that is $\forall (r_i, r_j) \in {\cal R_{\cal C}}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$, 
      we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$

@@

%       A {\bf conflict graph} represents the collision between the routes of $ {\cal R}_{\cal C}$. The vertices of a conflict graph $G = (V,E)$ are the routes of $ {\cal R}_{\cal C}$, and there is an edge between two vertices if and only if there is a common arc between the two routes in $ {\cal R}_{\cal C}$.
%       
%       Given $u$ and $v$ two vertices of the conflict graph, corresponding to two routes colliding in $ {\cal R}_{\cal C}$. The weight of an edge, $w(u,v)$, is the absolute value of the difference between the distance of the two routes between their respective source node and the collision point.
%       
%       A labeling $F$ of such a graph is an affectation of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.
      \begin{figure}[h]
       \begin{center}

\tikzset{
  LabelStyle/.style = { rectangle, rounded corners, draw,
                       font = \bfseries },
  EdgeStyle/.append style = {->} }
  \SetGraphUnit{5}
  \node[draw,circle] (s3) at (4, 2) {$s_3$}; 
  \node[draw,circle] (s2) at (0, 4) {$s_2$}; 
  \node[draw,circle] (s1) at (0, 6) {$s_1$};

  \node[draw,circle] (t3) at (14, 7) {$t_3$}; 
  \node[draw,circle] (t2) at (14, 4) {$t_2$}; 
  \node[draw,circle] (t1) at (10, 2) {$t_1$};

  \SetVertexNoLabel
  \Vertex[x=2,y=5]{A}
  \Vertex[x=4,y=5]{B}
  \Vertex[x=10,y=5]{C}
  \Vertex[x=12,y=5]{D}
  \Vertex[x=6,y=3]{E}
  \Vertex[x=8,y=3]{F}
  \tikzset{
  EdgeStyle/.append style = {green} }
  \Edge[label = 2](s2)(A)
  \Edge[label = 1](A)(B)
  \Edge[label = 2](B)(C)
  \Edge[label = 1](C)(D)
  \Edge[label = 1](D)(t2)

   \tikzset{
  EdgeStyle/.append style = {red} }
  \Edge[label = 2](s3)(E)
  \Edge[label = 1](E)(F)
  \Edge[label = 1](F)(C)
  \Edge[label = 1](C)(D)
  \Edge[label = 1](D)(t3) 
     \tikzset{
  EdgeStyle/.append style = {blue} }
  \Edge[label = 1](s1)(A)
  \Edge[label = 1](A)(B)
  \Edge[label = 1](B)(E)
  \Edge[label = 1](E)(F)
  \Edge[label = 1](F)(t1)

\end{tikzpicture}
      \end{center}
       \caption{A routage graph with $(0,\dots,0)$ as a $(2,1)$-periodic affectation}
      \end{figure}

@@

	\begin{lemma} 
	 For any odd $P$, there is a routage graph such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
	\end{lemma}
\begin{proof}

      Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
      We change the delays so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$. In such a graph, there is no $(P,\tau)$-periodic affectation, because of $P < n$.\\
      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R_{\cal C}}$.

@@

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
      and two disjoint subsets of vertices $S$ and $T$ of equal cardinality, where $S$ is the set of RRHs and $T$ is the set of BBUs. 
      A \textbf{symmetric} assignment ${\cal C}$, is an involutive function from $S$ to $T$, which maps each element $s\in S$ to ${\cal C}(s)$ and ${\cal C}(s)$ to $s$. It can also be seen as the set of pairs $(s,{\cal C}(s))$ and $({\cal C}(s),s)$.\\
      The Routing function ${\cal R}$ associates to each couple $(s,{\cal C}(s))$ a route called $r_s$ and to each couples $({\cal C}(s),s)$ a route called $r_{{\cal C}(s)}$.\\     
       We are given a period $P$, a routing function ${\cal R}$, and we consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_s$ to the route $r_s$ which begins by $s$, and $m_{C(s)}$ to the routes $r_{C(s)}$ which begins by $C(s)$.  This affectation represents the following process: first a message is sent at $s$, through the route $r_s$, at time $m_s$.
